A Wait-Free Queue with Polylogarithmic Step Complexity

### 2023-06-19 presentation/podc-presentation.tex
minor changes

@@

\Red{Double Refresh}:\\
If your CAS on $v$ fails twice, then\\
another process has propagated your operation to $v$.

>>>>

\newcommand{\itemnum}[1]{% reproduce beamer numbers as in enumerated lists
\setcounter{enumi}{#1}\usebeamertemplate{enumerate item}% 
}

@@

\begin{block}{Double Refresh}
If your CAS on $v$ fails twice, then\\
another process has propagated your operation to $v$.
\end{block}
